---
title: "HW3"
author: "Tuul Purevjav"
date: "3/02/2022"
output: html_document
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

We're planning to move to Washington state this summer.  The approximate area we'd like to move to is in King county.  We have two school-age kids and choosing a school for them is our starting point.  For this assignment, I made an interactive map showing 534, K-12 public schools in King county. On the map each school marker has a pop-up feature showing school name, address, phone and the school district information.  Once I choose a school I can potentially find housing close to the school by surveying the surrounding area.  My data source is at https://geo.wa.gov/datasets/k12wa::washington-state-public-schools/about. 

```{r message = FALSE}
library(tidyverse)
library(leaflet)
```

```{r}
# prepare the data
datain <- read.csv("Washington_State_Public_Schools.csv")
datain <- datain %>% 
  select(Latitude, Longitude, Name =`SchoolName`, District=`LEAName`, Address=`PhysicalAddress`, County, Phone) 
```

```{r}
# filter the data for King County
school <- datain %>% filter(County == 'King')
```


```{r}
# display school information
labs <- lapply(seq(nrow(school)), 
               function(i) {
  paste0( "", "Name: ",as.character(school[i, "Name"]), '<br>',
          "Address: ", as.character(school[i, "Address"]), '<br>',
          "Phone: ", as.character(school[i, "Phone"]), '<br>',
          "District: ",as.character(school[i, "District"]), '<br>',
          '' ) 
})
```

Since I have lot of data points that are close to each other, I used addAwesomeMarkers() function with clusterOptions argument, so that my map doesn't look too busy.  I also chose the default tile that addTiles() gives because it shows the surrounding areas with greater details with colors.  
```{r}
# create map with `leaflet`
map <- leaflet(school) %>%
  addTiles() %>%
  addAwesomeMarkers(~Longitude, ~Latitude,
                    label = ~lapply(labs, htmltools::HTML),
                    clusterOptions = markerClusterOptions())
map
```




